Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2025-08-20 src/docs_paper-jtb/paper.Rmd
Add cite

Independent logistic regression models are specified for HIV prevalence and ART coverage in the general population such that $\text{logit}(\rho_i) = \eta^\rho_i$ and $\text{logit}(\alpha_i) = \eta^\alpha_i$.
HIV incidence rate is modelled by $\log(\lambda_i) = \eta^\lambda_i$ and depends on adult HIV prevalence and adult ART coverage.
The structured additive predictors $\eta^\theta_i$ for $\theta \in \{\rho, \alpha, \lambda\}$ are given in Appendix 1.
The proportion recently infected $\kappa_i$ is linked to HIV incidence via a reformulation of the Kassanjee \textit{et al.} biomarker-based incidence estimator (INSERT REFERENCE: https://pubmed.ncbi.nlm.nih.gov/22627902/):

>>>>

Independent logistic regression models are specified for HIV prevalence and ART coverage in the general population such that $\text{logit}(\rho_i) = \eta^\rho_i$ and $\text{logit}(\alpha_i) = \eta^\alpha_i$.
HIV incidence rate is modelled by $\log(\lambda_i) = \eta^\lambda_i$ and depends on adult HIV prevalence and adult ART coverage.
The structured additive predictors $\eta^\theta_i$ for $\theta \in \{\rho, \alpha, \lambda\}$ are given in Appendix 1.
The proportion recently infected $\kappa_i$ is linked to HIV incidence via a reformulation of the biomarker-based incidence estimator of @kassanjee2012new
